---
title: "Bill Sampras Summer Job Decision"
author: "Sangho Lee"
date: ' '
output:
  html_document:
    df_print: paged
editor_options: 
  markdown: 
    wrap: sentence
---

```{css, echo=FALSE}
body {
  font-family: 'Verdana', sans-serif;
}

#footer {
position: fixed;
left: 0;
bottom: 0;
width: 100%;
background-color: #f2f2f2; /* You can change the background color */
  color: black; /* Text color */
  text-align: center;
padding: 10px 0;
font-size: 1.2em;
}

```

------------------------------------------------------------------------

------------------------------------------------------------------------

# **Case Summary**
<br><br>

**Note:** *This summary offers a creatively rephrased perspective of the
original case study. It aims to provide an engaging and understandable
narrative.*

# **Bill Sampras' Summer of Decisions: Navigating Career Crossroads** <br><br>

**Part 1**<br>
Bill Sampras, a diligent MBA student at MIT's Sloan School of Management, was at a pivotal crossroads. With a summer looming ahead and two potential job opportunities knocking at his door, Bill faced a decision that could shape his career path. Armed with experience and ambition, he embarked on a journey to weigh his options and make a choice that aligned with his aspirations.<br><br>

**Part 2**<br>
The first contender was a familiar one - a return to his roots at the company where he'd spent four impactful years. His former boss, John Mason, offered him a secure but time-sensitive summer position. This option represented safety and familiarity but came with a deadline that pressured Bill for an early decision.<br><br>

**Part 3**<br>
On the other side was a conversation with Vanessa Parker, Vice President of a prestigious investment banking firm. This chance encounter on a flight to Boston had opened the door to a potentially lucrative and prestigious summer role. However, this opportunity was shrouded in uncertainty, with details only to be revealed in the future, testing Bill's patience and risk tolerance.<br><br>

**Part 4**<br>
In the realm of uncertainty, Bill turned to decision analysis, constructing a decision tree to map out his possible paths. Each branch represented a choice, each node a consequence. This analytical approach transformed his dilemma from a confusing puzzle into a structured set of sequential decisions and possible outcomes.<br><br>

**Part 5**<br>
As Bill navigated this tree of possibilities, he considered not just the immediate choices but also the potential ramifications each path held. His decision was not merely about choosing a job; it was about setting a precedent for how he would confront and make significant career decisions under uncertainty.<br><br>

**Part 6**<br>
With the decision tree complete and the options laid bare, Bill stood ready to make a choice. His journey through this analytical process was more than just a method to pick a summer job; it was a transformative experience that equipped him with the tools and mindset to tackle future uncertainties. Bill's summer of decisions was a testament to the power of strategic thinking and the profound impact that thoughtful analysis can have on shaping one's professional journey.<br><br>



### Below, I will outline the nodes to construct the decision tree. Here are the bullet points detailing Bill's job-related decision problem.

#### <br> [I will use DiagrammeR package to construct the decision tree.]{style="color:orange"}

<br>

#### Start Node: Bill's initial decision.

#### Decision 1: Accept John's offer.

-   Outcome: Secures a summer job with a known salary of \$12,000.

-   No further decisions: Path ends here.

#### Decision 2: Reject John's offer.

-   Event A: Vanessa's firm offers Bill a job.

1.  Decision A1: Accept Vanessa's offer.
    Outcome: Secures a job with Vanessa, salary unknown but potentially higher.

2.  Decision A2: Reject Vanessa's offer.
    Subsequent Decision: Look for a job through the school's corporate summer recruiting program.
    Outcome: Finds a job through the program, salary and position uncertain.

-   Event B: Vanessa's firm does not offer Bill a job.
    Subsequent Decision: Look for a job through the school's corporate summer recruiting program.

-   Outcome: Finds a job through the program, salary and position uncertain.

    <br>

In R, the DiagrammeR package includes a function known as grViz.

<br>

```{r}
library(DiagrammeR)

DiagrammeR::grViz("
digraph decision_tree {

  # Define node styles
  node [fontname = Helvetica, shape = box]
  edge [fontname = Helvetica]

  # Start Node
  Start [label='Start Node: Bill’s initial decision.']

  # Decision Nodes
  Decision1 [label='Decision 1: Accept John’s offer.']
  Decision2 [label='Decision 2: Reject John’s offer.']
  EventA [label='Event A: Vanessa’s firm offers Bill a job.', shape = ellipse]
  EventB [label='Event B: Vanessa’s firm does not offer Bill a job.', shape = ellipse]
  DecisionA1 [label='Decision A1: Accept Vanessa’s offer.']
  DecisionA2 [label='Decision A2: Reject Vanessa’s offer.']
  Recruiting [label='Look for a job through the school’s program', shape = box3d]

  # Outcome Nodes
  Outcome1 [label='Outcome: Job with John, $12,000.', shape = plaintext]
  Outcome2 [label='Outcome: Job with Vanessa, salary unknown.', shape = plaintext]
  Outcome3 [label='Outcome: Job through program, salary and position uncertain.', shape = plaintext]

  # Connect nodes with edges
  Start -> Decision1 
  Start -> Decision2 
  Decision1 -> Outcome1 
  Decision2 -> EventA 
  Decision2 -> EventB 
  EventA -> DecisionA1 
  EventA -> DecisionA2 
  EventB -> Recruiting 
  DecisionA1 -> Outcome2 
  DecisionA2 -> Recruiting 
  Recruiting -> Outcome3 
}
", width = 1600, height = 800)



```

#### 

#### Node is designed to help Bill visualize his dilemma comprehensively, yet the ultimate decision hinges on his personal judgment and preferences, as well as additional information such as the success rate of the school's job program.

#### Ultimately, Bill's choice will be influenced by his preferences or gut feeling. For those inclined towards a more secure route, accepting John's offer might seem sensible. On the other hand, risk-takers might prefer exploring other options in the decision tree.

#### To make this activity a little more fun, let's consider a hypothetical scenario, In the book, it provides some probabilites the chance that Vanessa will offer a job, and Bill also has gathered the information from the Sloan School what the previuse students were offered.

<br>

#### [- The chance of receiving an offer from John: 100%]{style="color:blue"}

#### [- The expected income: \$12,000]{style="color:blue"}

#### [- The probability of receiving Vanessa's offer: 60%]{style="color:blue"}

#### [- The anticipated income: \$14,000]{style="color:blue"}

#### [- The likelihood of obtaining a job through the school's program: 95%]{style="color:blue"}

#### [- The potential income range: \$6,000 to \$21,600]{style="color:blue"}

### <br>

```{r}
# Probabilities and incomes
prob_john_offer <- 1.0 
income_john <- 12000

prob_vanessa_offer <- 0.60  
income_vanessa <- 14000

prob_school_program <- 0.95  
income_school_program_avg <- (6000 + 21600) / 2

# Calculate expected values
expected_value_john <- prob_john_offer * income_john

# For Vanessa's path, if she doesn't offer, then Bill goes to the school program
expected_value_vanessa <- prob_vanessa_offer * income_vanessa + 
                         (1 - prob_vanessa_offer) * prob_school_program * income_school_program_avg

# For the school program directly (rejecting both John and Vanessa)
expected_value_school <- prob_school_program * income_school_program_avg

# Print the expected values
print(expected_value_john)
print(expected_value_vanessa)
print(expected_value_school)

```

```{r}
grViz("
digraph decision_tree {

  # Define node styles
  node [fontname = Helvetica, shape = box]
  edge [fontname = Helvetica]

  # Start Node
  Start [label='Start Node: Bill’s initial decision.']

  # Decision Nodes
  Decision1 [label='Decision 1: Accept John’s offer.\\nProb: 100%\\nExpected: $12,000']
  Decision2 [label='Decision 2: Reject John’s offer.']
  EventA [label='Event A: Vanessa’s firm offers Bill a job.\\nProb: 60%', shape = ellipse]
  EventB [label='Event B: Vanessa’s firm does not offer Bill a job.\\nProb: 40%', shape = ellipse]
  DecisionA1 [label='Decision A1: Accept Vanessa’s offer.\\nProb: 60%\\nExpected: $14,000']
  DecisionA2 [label='Decision A2: Reject Vanessa’s offer.\\nLook for a job through the school’s program']
  Recruiting [label='Engage with the school’s program\\nProb: 95%\\nExpected Range: $6,000 - $21,600', shape = ellipse]

  # Outcome Nodes
  Outcome1 [label='Outcome: Job with John, $12,000.', shape = plaintext]
  Outcome2 [label='Outcome: Job with Vanessa, $13,644\\n(If offered)', shape = plaintext]
  Outcome3 [label='Outcome: Job through program, $13,110\\n(Probability weighted avg: $(income_school_program_avg))', shape = plaintext]

  # Connect nodes with edges
  Start -> Decision1 
  Start -> Decision2 [color=red, penwidth=2.0] 
  Decision1 -> Outcome1 
  Decision2 -> EventA [color=red, penwidth=2.0] 
  Decision2 -> EventB 
  EventA -> DecisionA1 [color=red, penwidth=2.0] 
  EventA -> DecisionA2 
  EventB -> Recruiting 
  DecisionA1 -> Outcome2 [color=red, penwidth=2.0] 
  DecisionA2 -> Recruiting 
  Recruiting -> Outcome3 
}
", width = 1600, height = 800)

```

#### Given these result, the path with the highest expected value is [waiting for Vanessa's offer]{style="color:blue"}, with an expected value of [\$13,644.]{style="color:blue"}

#### However, it's important to note that this path also carries more risk, as it relies on the 75% probability of receiving Vanessa's offer. If security is a primary concern, [accepting John's offer]{style="color:blue"} would be the most secure choice, being cool with a lower expected value [\$12,000.]{style="color:blue"}

#### <br> [What decision would you make in this situation, and what does it reflect about your character? Are you more of a risk-taker or someone who seeks stability and security?]{style="color:purple"}

<br>

#### *This decision-making code in R is quite robust when equipped with certain probabilities. I'm sure you've encountered many scenarios in various industries where choosing the right path depended on probabilities. If you find yourself in a situation similar to Bill Sampras' but in your own business context, you might consider drawing your own decision tree to identify the path that yields the greatest value.*

<br> <br>

------------------------------------------------------------------------

------------------------------------------------------------------------

::: {#footer}
```{r echo=FALSE, results='asis'}
cat("Copyright © 2023-", format(Sys.Date(), "%Y"), "Sangho Lee, All rights reserved.")
```
:::
